SDSS-GAIA Calibration Note

### 2022-08-11 ms.tex

\section{Basic Statistics}
\begin{deluxetable*}{rrrrrrr}[ht]
\tablehead{
\colhead{Survey}&
\colhead{Number of Plates}&
\colhead{Number of Spectra}&
\colhead{Missing}&
\colhead{Star}&
\colhead{Quasar}&
\colhead{Galaxy}
}
\startdata
SDSS-DR8 & 3,685 & 1,712,809 & 130,391 & 605,884& 142,232& 964,693\\
SDSS-DR17 & 4,131 & 3,541,517 & 406,483 & 499,127 & 963,616 & 2,078,774\\
\hline
GAIAXP-DR8 & 2,782 & 272,729&  & 240,470& 32,259 & N/A \\
GAIAXP-DR17 & 3,950 & 88,915  &  & 63,083 & 25,832 & N/A
\enddata
\end{deluxetable*}

In 'spobj\_dr8.fits', 1,843,200 objects are listed, but some do not have thing\_id, and we are missing 100,000 objects.

3,948,000

>>>>

\section{Basic Statistics}
In 'spobj\_dr8.fits', 1,843,200 objects are listed, but some do not have thing\_id, and we are missing 130,391 objects.
DR17, spall file contains 3,948,000 spectra, but if we exclude thing\_id=-1, 406,483 objects are dropped out.
We note, we have a more stellar spectra in DR8 than DR17.

We collected GAIA XP spectra which is a low resolution spectra and becomes public for the first time in June 2022.  In the second half of Table \ref{tbl:summary}, we summarize the number statistics of objects which has both GAIA XP and SDSS spectra.

\begin{deluxetable*}{rrrrrrr}[ht]
\label{tbl:summary}
\title{GAIA-SDSS Spectra Summary}
\tablecaption{Top half shows the number of spectra for DR8 and DR17.  The second half shows the number of GAIA XP spectra which has SDSS spectra}
\tablehead{
\colhead{Survey}&
\colhead{Number of Plates}&
\colhead{Number of Spectra}&
\colhead{Missing}&
\colhead{Star}&
\colhead{Quasar}&
\colhead{Galaxy}
}
\startdata
SDSS-DR8 & 3,685 & 1,712,809 & 130,391 & 605,884& 142,232& 964,693\\
SDSS-DR17 & 4,131 & 3,541,517 & 406,483 & 499,127 & 963,616 & 2,078,774\\
\hline
GAIAXP-DR8 & 2,782 & 272,729&  & 240,470& 32,259 & N/A \\
GAIAXP-DR17 & 3,950 & 88,915  &  & 63,083 & 25,832 & N/A
\enddata
\end{deluxetable*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=270,width=8.9cm]{figures/120821_01_airmass_vs_dmag_star_dr8.png}
\includegraphics[angle=270,width=8.9cm]{figures/120821_04_airmass_vs_dmag_quasar_dr8.png}
\caption{DR8: Comparison of Synthetic Magnitude from Model Spectrum and PSF magnitude as a function of airmass. Stars and Quasars are shown left and right respectively.  We do not see any trend, and in general, spectra are well flux calibrated.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=270,width=8.9cm]{figures/120821_02_airmass_vs_dmag_star_dr9_redfiber.png}
\includegraphics[angle=270,width=8.9cm]{figures/120821_05_airmass_vs_dmag_quasar_dr9_redfibers.png}
\caption{DR9 lambda$\_$eff=5400 : Starting SDSS-III, spectrograph is upgraded.  To enhance S/N in blue, a slight offset of fiber position is introduced as well as washers.  Two fiber positions are named lambda$\_$eff=4000 and 5400.  What is shown here is the case for lambda$\_$eff=5400 which is the same as SDSS DR8.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=270,width=8.9cm]{figures/120821_03_airmass_vs_dmag_star_dr9_bluefiber.png}
\includegraphics[angle=270,width=8.9cm]{figures/120821_06_airmass_vs_dmag_quasar_dr9_bluefiber.png}
\caption{DR9 lambda$\_$eff=4000 : Now, the problem emerges. Enhancing S/N in blue sacrifices the flux calibration.  Washer has 3 layers, z=0, z=175, and z=300 from inner part to outskirts.  When elevation is low, namely airmass is high, hour angle difference becomes eminent, and flux calibration gets difficult.}
\end{center}
\end{figure*}
